Research Proposal: Specialization Trends in Economics Research using JEL Codes \\ Text Data in Economics by Aapo Stenhammar \\ University of Bonn, Winter Term 2024/25

### 2025-02-27 documents/paper.tex
Adapt width of figure and remove comments from text_model task.

\begin{figure}
    \centering
    \includegraphics{../bld/figures/fig_dp_counts}
    \caption{Number of Discussion Papers \& JEL Codes per Discussion Paper}
    \label{fig:dp_counts}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{../bld/figures/fig_author_trends}
    \caption{Average Number of Authors Over Time}
    \label{fig:author_trends}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{../bld/figures/fig_topic_trends}
    \caption{Top 5 Topics Increasing (Left) and Decreasing (Right) in Presence}
    \label{fig:top5_increasing_decreasing_topics}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{../bld/figures/fig_top5overall_jel}
    \caption{Top 5 JEL Codes}
    \label{fig:top5overall_jel}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{../bld/figures/fig_top3yearly_jel}
    \caption{Top 3 JEL Codes yearly}
    \label{fig:top3yearly_jel}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{../bld/figures/fig_counts_dp_jel_codes}
    \caption{Discussion Papers by Author \& Discussion Papers by JEL Codes}
    \label{fig:counts_dp_jel_codes}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../bld/figures/fig_dp_counts}
    \caption{Number of Discussion Papers \& JEL Codes per Discussion Paper}
    \label{fig:dp_counts}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../bld/figures/fig_author_trends}
    \caption{Average Number of Authors Over Time}
    \label{fig:author_trends}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../bld/figures/fig_topic_trends}
    \caption{Top 5 Topics Increasing (Left) and Decreasing (Right) in Presence}
    \label{fig:top5_increasing_decreasing_topics}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../bld/figures/fig_top5overall_jel}
    \caption{Top 5 JEL Codes}
    \label{fig:top5overall_jel}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../bld/figures/fig_top3yearly_jel}
    \caption{Top 3 JEL Codes yearly}
    \label{fig:top3yearly_jel}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{../bld/figures/fig_counts_dp_jel_codes}
    \caption{Discussion Papers by Author \& Discussion Papers by JEL Codes}
    \label{fig:counts_dp_jel_codes}
\end{figure}
